\bibliographystyle{alpha}
\bibliography{bibliografia}
\begin{thebibliography}{1}

\bibitem{Reynolds87}
C. W. Reynolds
\newblock {\em Flocks, Herds, and Schools: A Distributed Behavioral Model}.
\newblock Computer Graphics, 21(4), Lipiec 1987, str. 25-34

\bibitem{BeniWang89}
G. Beni, J. Wang
\newblock {\em Swarm Intelligence in Cellular Robotic Systems}.
\newblock NATO Advanced Workshop on Robots and Biological Systems, Włochy, Lipiec 1989

\bibitem{KennedyEberhart95}
J. Kennedy, R. Eberhart
\newblock {\em Particle Swarm Optimization}.
\newblock Proceedings of IEEE International Conference on Neural Networks IV, 1995, str. 1942–1948


\bibitem{ABC}
D. Karaboga
\newblock {\em An Idea Based On Honey Bee Swarm for Numerical Optimization}.
\newblock  Technical Report-TR06, Erciyes University, Engineering Faculty, Computer Engineering Department, Turcja, 2005


\bibitem{BA}
D.T. Pham, A. Ghanbarzadeh, E. Koç, S. Otri , S. Rahim , M. Zaidi 
\newblock {\em The Bees Algorithm – A Novel Tool for Complex Optimisation Problems}.
\newblock Technical Note, Manufacturing Engineering Centre, Cardiff University, Wielka Brytania, 2005


\bibitem{ACO2}
X. Hu, J. Zhang, Y. Li
\newblock {\em Orthogonal methods based ant colony search for solving continuous optimization problems}.
\newblock Journal of Computer Science and Technology, Springer, Styczeń 2008, str. 2-28


\bibitem{ACO}
M. Dorigo, L.M. Gambardella
\newblock {\em Ant Colony System : A Cooperative Learning Approach to the Traveling Salesman Problem}.
\newblock IEEE Transactions on Evolutionary Computation, 1997, str. 53-66


\bibitem{ALO}
S. Mirjalili
\newblock {\em The Ant Lion Optimizer}.
\newblock Advances in Engineering Software 83, 2015, str. 80–98.


\bibitem{PSOneighbourhood}
P.N. Suganthan
\newblock {\em Particle swarm optimiser with neighbourhood operator}.
\newblock Evolutionary Computation, IEEE, Washington, 1999


\bibitem{PSOrandom}
M. Clerc
\newblock {\em Standard Particle Swarm Optimisation}.
\newblock HAL open access archive, 2012


\bibitem{PSOparams}
Y. Shi, R.C. Eberhart
\newblock {\em Parameter selection in particle swarm optimization}.
\newblock Evolutionary Computation, IEEE, Washington, 1999
Proceedings of Evolutionary Programming VII (EP98), 1998


\bibitem{PSOvelocity}
R.C. Eberhart, Y. Shi
\newblock {\em Comparing inertia weights and constriction factors in particle swarm optimization}.
\newblock Proceedings of the Congress on Evolutionary Computation 1, 2000


\bibitem{GA1}
G.E.P. Box 
\newblock {\em Evolutionary operation: A method for increasing industrial productivity}.
\newblock Appl. Statistics, vol. VI, no.2, 1957, str. 81–101


\bibitem{GA2}
J. H. Holland
\newblock {\em Adaptation in Natural and Artificial Systems}.
\newblock  University of Michigan Press, Ann Arbor, 1975


\bibitem{EMASweb}
A. Byrski, R. Dreżewski, M. Kisiel-Dorohinicki, L. Siwik
\newblock {\em Evolutionary Multi-Agent Systems}.
\newblock  AGH University of Science and Technology, 2012
\newblock \\\texttt{https://age.iisg.agh.edu.pl/emas/emas.html}.


\bibitem{emas1}
K. Cetnarowicz, M. Kisiel-Dorohinicki, E. Nawarecki
\newblock {\em The application of evolution process in multi-agent world (MAW) to the prediction system}.
\newblock  M. Tokoro, editor, Proc. of the 2nd Int. Conf. on Multi-Agent Systems (ICMAS'96). AAAI Press, 1996


\bibitem{emas2}
 A. Byrski, R. Drezewski, L. Siwik, M. Kisiel-Dorohinicki
\newblock {\em Evolutionary multiagent systems}.
\newblock The Knowledge Engineering Review, 2013


\bibitem{emas3}
M. Kisiel-Dorohinicki
\newblock {\em Agent-oriented model of simulated evolution}.
\newblock In William I. Grosky and Frantisek Plasil, editors, SofSem 2002: Theory and Practice of Informatics, volume 2540 of LNCS. Springer-Verlag, 2002.


\bibitem{rastrigin}
Wikimedia Commons
\newblock {\em Rastrigin function}.
\newblock \\\texttt{http://commons.wikimedia.org/wiki/File:Rastrigin function.png}.


\bibitem{agentowyemas}
M. Kisiel-Dorohinicki
\newblock {\em Agentowe architektury populacyjnych systemów inteligencji obliczeniowej}.
\newblock Rozprawy monograficzne 269, Wydawnictwo AGH, Kraków, 2013


\bibitem{opisagenta}
S. Franklin, A. Graesser
\newblock {\em Is it an agent or just a program?: A taxonomy for antonomous agents.}.
\newblock Intelligent Agents III vol. 1193, LNAI. Springer-Verlag, 1997


\bibitem{systemagentowy}
M. Wooldridge
\newblock {\em Agent-based Software Engineering.}.
\newblock IEEE Trans. on Software Engineering, vol. 144, no. 1, 1997


\bibitem{pyage}
M. Kaziród, W. Korczynski, A. Byrski.
\newblock {\em Agent-oriented computing platform in python.}.
\newblock  Web Intelligence (WI) and Intelligent Agent Technologies (IAT), 2014 IEEE/WIC/ACM International Joint Conferences on, vol. 3, pages 365-372. IEEE, 2014


\bibitem{rastrigin}
L. A. Rastrigin
\newblock {\em Systems of extremal control.}.
\newblock Nauka, Moskwa, 1974


\bibitem{rastrigin2}
 H. Mühlenbein, D. Schomisch, J. Born
\newblock {\em The Parallel Genetic Algorithm as Function Optimizer.}.
\newblock Parallel Computing, 17, 1991


\bibitem{roznorodnosckisiel}
M. Kisiel-Dorohinicki
\newblock {\em Evolutionary multi-agent systems in non-stationary environments.}
\newblock Computer Science 14, 2013


\bibitem{roznorodnoscmoi}
R. W. Morrison, K. A. D. Jong 
\newblock {\em Measurement of Population Diversity. In: Artificial Evolution.}
\newblock 5th Int. Conf., Evolution Artificielle, EA 2001, P. Collet, et al., eds., LNCS, vol. 2310, Springer, 2002


\bibitem{listaswarm}
I. Fister, X.S. Yang, J. Brest, D. Fister
\newblock {\em A Brief Review of Nature-Inspired Algorithms for Optimization.}
\newblock Elektrotehniski Vestnik, 80 , 2013

\bibitem{pyagestrona}
M. Kaziród
\newblock {\em pyAgE github}.
\newblock \\\texttt{https://github.com/maciek123/pyage}.

\bibitem{psowstep}
U. Boryczka
\newblock {\em Inteligencja stadna}.
\newblock \\\texttt{http://155.158.112.34/algorytmyewolucyjne/materialy/inteligencja stadna.pdf}.

\end{thebibliography}
